Model_CFU

### 2016-12-05 code/HumanCdGF_model_cfu.Rmd
include source/cage

### - Uncorrelated OTUs + source
cfu_uncor_src_shared_df <- colonized_cfu %>% 
    right_join(community_d0.df) %>% 
    select(-mouse_id, -cage_id) %>% 
    filter(!is.na(log_cfu_med))
cfu_uncor_src_shared_df$cage_id <- as.factor(cfu_uncor_src_shared_df$cage_id)
set.seed(seed)
cfu_uncor_src_cage_rf <- rfe(cfu_uncor_src_shared_df[ , -2], cfu_uncor_src_shared_df$log_cfu_med,
                 sizes = subsets,
                 rfeControl = rfe_ctrl)
cfu_uncor_src_cage_features <- predictors(cfu_uncor_src_cage_rf)
cfu_uncor_src_cage_model <- cfu_uncor_src_cage_rf$fit
#rf_prediction <- data.frame(observed = cfu_uncor_shared_df$log_cfu_med, 
#                       predicted = rf_n_features$predicted)
#rf_prediction <- merge(rf_prediction, colonized_cfu, by.x = 'observed', by.y = 'log_cfu_med')

### - All OTUs + source
cfu_all_src_cage_shared_df <- colonized_cfu %>% 
    right_join(community_all_d0) %>% 
    select(-mouse_id, -cage_id) %>% 
    filter(!is.na(log_cfu_med))
cfu_all_src_cage_shared_df$cage_id <- as.factor(cfu_all_src_cage_shared_df$cage_id)
set.seed(seed)
cfu_all_src_cage_rf <- rfe(cfu_all_src_cage_shared_df[ , -2], cfu_all_src_cage_shared_df$log_cfu_med,
                 sizes = subsets,
                 rfeControl = rfe_ctrl)
cfu_all_src_cage_features <- predictors(cfu_all_src_cage_rf)
cfu_all_src_cage_model <- cfu_all_src_cage_rf$fit

### - Uncorrelated OTUs + source/cage
cfu_uncor_cg_src_shared_df <- colonized_cfu %>% 
    right_join(community_d0.df) %>% 
    select(-mouse_id) %>% 
    filter(!is.na(log_cfu_med))
cfu_uncor_cg_src_shared_df$cage_id <- as.factor(cfu_uncor_cg_src_shared_df$cage_id)
set.seed(seed)
cfu_uncor_cg_src_cage_rf <- rfe(cfu_uncor_cg_src_shared_df[ , -3], cfu_uncor_cg_src_shared_df$log_cfu_med,
                 sizes = subsets,
                 rfeControl = rfe_ctrl)
cfu_uncor_cg_src_cage_features <- predictors(cfu_uncor_cg_src_cage_rf)
cfu_uncor_cg_src_cage_model <- cfu_uncor_cg_src_cage_rf$fit
#rf_prediction <- data.frame(observed = cfu_uncor_shared_df$log_cfu_med, 
#                       predicted = rf_n_features$predicted)
#rf_prediction <- merge(rf_prediction, colonized_cfu, by.x = 'observed', by.y = 'log_cfu_med')

### - All OTUs + source/cage
cfu_all_cg_src_cage_shared_df <- colonized_cfu %>% 
    right_join(community_all_d0) %>% 
    select(-mouse_id) %>% 
    filter(!is.na(log_cfu_med))
cfu_all_cg_src_cage_shared_df$cage_id <- as.factor(cfu_all_cg_src_cage_shared_df$cage_id)
set.seed(seed)
cfu_all_cg_src_cage_rf <- rfe(cfu_all_cg_src_cage_shared_df[ , -3], cfu_all_cg_src_cage_shared_df$log_cfu_med,
                 sizes = subsets,
                 rfeControl = rfe_ctrl)
cfu_all_cg_src_cage_features <- predictors(cfu_all_cg_src_cage_rf)
cfu_all_cg_src_cage_model <- cfu_all_cg_src_cage_rf$fit

@@

##### All OTUs  
Model:  
`r cfu_all_model`  
Features:  
`r cfu_all_features`

####  All OTUs + Cage
Model:  
`r cfu_all_cage_model`  
Features:  
`r cfu_all_cage_features`

####  Uncorrelated OTUs
Model:  
`r cfu_uncor_model`  
Features:  
`r cfu_uncor_features`

####  Uncorrelated OTUs + Cage
Model:  
`r cfu_uncor_cage_model`  
Features:  
`r cfu_uncor_cage_features`

####  All OTUs + Source
Model:  
`r cfu_all_src_model`  
Features:  
`r cfu_all_src_features`

####  Uncorrelated OTUs + Source
Model:  
`r cfu_uncor_src_model`  
Features:  
`r cfu_uncor_src_features`

####  All OTUs + Source/Cage
Model:  
`r cfu_all_cg_src_model`  
Features:  
`r cfu_all_cg_src_features`

####  Uncorrelated OTUs + Source/Cage
Model:  
`r cfu_uncor_cg_src_model`  
Features:  
`r cfu_uncor_cg_src_features`

>>>>

### - Uncorrelated OTUs + source
cfu_uncor_src_shared_df <- colonized_cfu %>% 
    right_join(community_d0.df) %>% 
    select(-mouse_id, -cage_id) %>% 
    filter(!is.na(log_cfu_med))
cfu_uncor_src_shared_df$human_source <- as.factor(cfu_uncor_src_shared_df$human_source)
set.seed(seed)
cfu_uncor_src_rf <- rfe(cfu_uncor_src_shared_df[ , -2], cfu_uncor_src_shared_df$log_cfu_med,
                 sizes = subsets,
                 rfeControl = rfe_ctrl)
cfu_uncor_src_features <- predictors(cfu_uncor_src_rf)
cfu_uncor_src_model <- cfu_uncor_src_rf$fit
#rf_prediction <- data.frame(observed = cfu_uncor_shared_df$log_cfu_med, 
#                       predicted = rf_n_features$predicted)
#rf_prediction <- merge(rf_prediction, colonized_cfu, by.x = 'observed', by.y = 'log_cfu_med')

### - All OTUs + source
cfu_all_src_shared_df <- colonized_cfu %>% 
    right_join(community_all_d0) %>% 
    select(-mouse_id, -cage_id) %>% 
    filter(!is.na(log_cfu_med))
cfu_all_src_shared_df$human_source <- as.factor(cfu_all_src_shared_df$human_source)
set.seed(seed)
cfu_all_src_rf <- rfe(cfu_all_src_shared_df[ , -2], cfu_all_src_shared_df$log_cfu_med,
                 sizes = subsets,
                 rfeControl = rfe_ctrl)
cfu_all_src_features <- predictors(cfu_all_src_rf)
cfu_all_src_model <- cfu_all_src_rf$fit

### - Uncorrelated OTUs + source/cage
cfu_uncor_cg_src_shared_df <- colonized_cfu %>% 
    right_join(community_d0.df) %>% 
    select(-mouse_id) %>% 
    filter(!is.na(log_cfu_med))
cfu_uncor_cg_src_shared_df$cage_id <- as.factor(cfu_uncor_cg_src_shared_df$cage_id)
cfu_uncor_cg_src_shared_df$human_source <- as.factor(cfu_uncor_cg_src_shared_df$human_source)
set.seed(seed)
cfu_uncor_cg_src_rf <- rfe(cfu_uncor_cg_src_shared_df[ , -3], cfu_uncor_cg_src_shared_df$log_cfu_med,
                 sizes = subsets,
                 rfeControl = rfe_ctrl)
cfu_uncor_cg_src_features <- predictors(cfu_uncor_cg_src_rf)
cfu_uncor_cg_src_model <- cfu_uncor_cg_src_rf$fit
#rf_prediction <- data.frame(observed = cfu_uncor_shared_df$log_cfu_med, 
#                       predicted = rf_n_features$predicted)
#rf_prediction <- merge(rf_prediction, colonized_cfu, by.x = 'observed', by.y = 'log_cfu_med')

### - All OTUs + source/cage
cfu_all_cg_src_shared_df <- colonized_cfu %>% 
    right_join(community_all_d0) %>% 
    select(-mouse_id) %>% 
    filter(!is.na(log_cfu_med))
cfu_all_cg_src_shared_df$cage_id <- as.factor(cfu_all_cg_src_shared_df$cage_id)
cfu_all_cg_src_shared_df$human_source <- as.factor(cfu_all_cg_src_shared_df$human_source)
set.seed(seed)
cfu_all_cg_src_rf <- rfe(cfu_all_cg_src_shared_df[ , -3], cfu_all_cg_src_shared_df$log_cfu_med,
                 sizes = subsets,
                 rfeControl = rfe_ctrl)
cfu_all_cg_src_features <- predictors(cfu_all_cg_src_rf)
cfu_all_cg_src_model <- cfu_all_cg_src_rf$fit

@@

##### All OTUs

```{r all_otus}
print(cfu_all_model)
print(cfu_all_features)
```

####  All OTUs + Cage  
```{r all_cg}
print(cfu_all_cage_model)
print(cfu_all_cage_features)
```

####  Uncorrelated OTUs

```{r uncor}
print(cfu_uncor_model)
print(cfu_uncor_features)
```

####  Uncorrelated OTUs + Cage
```{r uncor_cg}
print(cfu_uncor_cage_model)
print(cfu_uncor_cage_features)
```

####  All OTUs + Source

```{r all_src}
print(cfu_all_src_model)
print(cfu_all_src_features)
```

####  Uncorrelated OTUs + Source

```{r uncor_src}
print(cfu_uncor_src_model)
print(cfu_uncor_src_features)
```

####  All OTUs + Source/Cage

```{r all_cg_src}
print(cfu_all_cg_src_model)
print(cfu_all_cg_src_features)
```

####  Uncorrelated OTUs + Source/Cage

```{r uncor_cg_src}
print(cfu_uncor_cg_src_model)
print(cfu_uncor_cg_src_features)
```
